
%Each objective is expected to make a significant contribution to the aim or aims. While it should straightforward to tie the aims of your project to the central thesis statement, it can be trickier to tie the objectives to the aims. This is what your significance section needs to set out.

%\begin{itemize}
%	\item The thesis is important to the reader (the stakeholder)
%	\item Achieving the aims supports the thesis
%	\item Achieving the objectives supports the aims
%\end{itemize}


The significance of this research will be described both from a theoretical and practical standpoint.

\subsection{Theoretical significance:}

The findings from this study contribute to the machine learning community by addressing some areas of misrepresentation of the closed-data questionnaire. Specifically this research sets out to address the problem of handling a range of different response data types all at the same time by introducing a fuzzy association rule mining approach. Although fuzzy ARM has been looked at in a very small number of papers they have neither found a solution to the time consuming task of creating membership functions statically nor attempted to improve upon the results by tuning the rule parameters using gradient descent. The research will also enrich the understanding of analysing questionnaire responses along a timeline.  

\subsection{Practical significance:}

Providing unnecessary medical assessments to candidates that are unsuitable for a role raises a number of issues to the selection process of our industry partner


\begin{itemize}
	\item The cost of providing the assessment can be prohibitive.
	\item As the candidate put forward for an assessment is usually a long way through the selection process suitable secondary candidate's are not always available. This may be because the other candidate has already found a new role. This can also lead to the even larger problem of having to initiate the candidate recruitment cycle all over starting with the initial interview stage. 
	\item The candidate that is unsuitable for the role may well be suitable for a different role but has now missed the opportunity to apply for that role.
\end{itemize}


% Example
%To date there has been little consideration of EIT in regimes with widely mismatched probe and coupling fields (Aim 1); exploring a solution, via a theoretical model, to the understanding of whether non-optical fields can control absorption (Objective 1) will open up feasibility studies of future low-power, compact experimental system useful for future quantum control systems.The development of such a system (Aim 2) will be underpinned by the first verification that EIT is possible in a widely mismatched system in rubidium vapour(Objective 2).To fully verify the model developed in Objective 1, polarization effects will be explored (Objective 3) with the goal of delivering finer control of the absorption of the probe beam via field control that is not dependent on changing the wavelength (Aim 3).